---
title: "rLambda -- run a R script on AWS Lambda"
author: "Sam"
date: "`r format(Sys.time(),'%B, %d, %Y')`"
output: html_document
vignette: >
  %\VignetteIndexEntry{Put the title of your vignette here}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The AWS Lambda function is registered for use by our group account. By default, 
AWS will look for credentials in the file `~/.aws/credentials`. This default 
can be overridden by setting environment variables `AWS_ACCESS_KEY_ID` and  
`AWS_SECRET_ACCESS_KEY`. 

The package uses the local directory for temporary file storage. It is recommended
that the user make an empty temporary directory to run in.

```{r}
# system("mkdir -p /tmp/testdir")
# setwd("/tmp/testdir")
# closeAllConnections()    # a wise precaution
```

Initialize python with the path to the desired python executable.

```{r}
library(rLambda)
rLambdaInitialize(path="/anaconda3/bin/python")
```

rLambda runs the no-parameter function `run()` in the current environment,
and assign the return value to `result`. 

This means the user should:

* Define a `run` function that takes no parameters.
* Avoid defining objects in the environment that `run` does not use.
* Design `run` to return an object and/or to assign objects to its enclosing environment.
* Avoid using the name `result` for an object that should not be overwritten.

```{r}
rm(list=ls())            # clean up
df <- data.frame(x = 1:10, y = 1:10 + rnorm(n=10))
run <- function()  {
  lm(y ~ x, df)
}
rLambdaExecute()
```

If no error occurs, there should be a `result` object in the local environment. 
However, this is not working at the moment, for reasons not yet understood. So 
we can load and use the response with:

```{r}
# load("newdata.Rdata")
# summary(result)
```

When the result has been used/saved, it may be a good idea to clean up, to prevent
leaving things in the execution directory that may interfere with subsequent 
executions.

```{r}
# setwd("~")
# system("rm -Rf /tmp/tempdir")
```








